---
title: "Model_Exercises"
author: "Daniel_Rivera"
date: "October 14, 2022"
output: html_document
---

Exercise 1
Familiarize yourself with the heights data set provided with the modelr package.
```{r}
#import modelr library and extract the heights file
library(modelr)
modelr::heights
```

Exercise 2
Create a list of formulas for modeling income with:
*height
*height * weight
*linear combination of all variables

```{r}
set.seed(1453)
#se the no. of observations
N <- 100 
#specify weight( in kg)
weight <- runif(n=N, min=60, max=100)
#specify height (in cm)
height <- 2.2*weight + rnorm(n=N, mean=0, sd=10)
#plot the weight vs height
plot(weight, height, pch=19, xlab='Weight (kg)', ylab='Height (cm)', col='grey')

## Using a Linear model fit
fit <- lm(height ~ weight)

## Plot the  model fit
plot(weight, height, pch=19,main= "Linear Model Fit of Weight vs. Height",xlab='Weight (kg)', ylab='Height (cm)', col='grey')
lines(weight, predict(fit), col='black', lwd=3)
```

Exercise 3
From the data, remove rows containing NA's. Fit the linear model with the formulas from exercise 2.
```{r}
#import necessary library to filter data
library(tidyr)
#Check the complete dataframe to determine if there are any NA's:
is.na(heights)
#Delete all the celse with NA
height.filtered <- na.omit(heights)
height.filtered
set.seed(1453)
#se the no. of observations
N <- 100 
#specify weight( in kg)
weight1 <- runif(n=N, min=60, max=100)
#specify height (in cm)
height1 <- 2.2*weight + rnorm(n=N, mean=0, sd=10)
#plot the weight vs height
plot(weight1, height1, pch=19, xlab='Weight (kg)', ylab='Height (cm)', col='grey')

## Using a Linear model fit
fit1 <- lm(height1 ~ weight1)

## Plot the  model fit
plot(weight1, height1, pch=19,main= "Linear Model Fit of Weight vs. Height",xlab='Weight (kg)', ylab='Height (cm)', col='grey')
lines(weight1, predict(fit1), col='black', lwd=3)
```

Exercise 4
For each fit, calculate RMSE.
```{r}
#First take a summary of our linear fit:
summary(fit)
#Calculate the RMSE by taking the mean of the square root of the residuals of the fit
sqrt(mean(fit$residuals^2))
```

Exercise 5
For each model, add residuals to the data and plot their distribution. (Hint: use lift_dl().)
```{r}
#res <- resid(fit1)
#plot(fit1, res, pch=19,main= "Linear Model Fit vs. Residuals",xlab='Model', ylab='Residuals', col='grey')
#lines(fit1, predict(fit1), col='black', lwd=3)

```

